Report on a Safety Checker for Petri nets

### 2014-01-31 paper/workspace/main.tex
Fixed typo in report

  # Place equations
  for s in S:
    # initial number of tokens
    print(s + " = " + M0(s)"
    for t in T:
      if (t, s) in E and not (s, t) in E:
        # input transition
        print(" + " t)
      if (s, t) in E and not (t, s) in E:
        # output transition
        print(" - " t)
    print("\n")

>>>>

  # Place equations
  for s in S:
    # initial number of tokens
    print(s + " = " + M0(s)"
    for t in T:
      if (t, s) in E and not (s, t) in E:
        # input transition
        print(" + " + t)
      if (s, t) in E and not (t, s) in E:
        # output transition
        print(" - " + t)
    print("\n")
